---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# M4comp2018

The R package M4comp2018 contains the 100000 time series from the M4-competition.
It also includes the true future values (the test part) and the  submitted forecasts of the top25 participants.

## Installation

Development version with the latest features:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("carlanetto/M4comp2018")
```


## Example


The `M4` object is a list with the series. Each element of this list is also a list with some components, like the 
series, the future values, type and domain and the submitted forecasts.

```{r}
## check the components of the least
library(M4comp2018)
data(M4)
names(M4[[1]])
#extract yearly series
yearly_M4 <- Filter(function(l) l$period == "Yearly", M4)
```

```{r}
#plot one of the series, in red the future data
#in black, the hitorical data
library(ggplot2)
library(forecast)
plot(ts(c(M4[[40773]]$x, M4[[40773]]$xx),
        start=start(M4[[40773]]$x), frequency = frequency(M4[[40773]]$x)),
        col="red", type="l", ylab="")
lines(M4[[40773]]$x, col="black")
```


```{r eval=FALSE}
#read the help file for documentation
?M4comp2018
```

You can check the point forecasts subissions in the `$pt_ff` of each element of the list. Info about the
submissions is in the submission_info dataframe, the order of `$pt_ff` is the OWA ranking. Upper and Lower bound prediction intervals are found in `$up_ff` and `$low_ff` respectively.

```{r eval=FALSE}
?submission_info
```

```{r eval=TRUE}
M4[[1]]$pt_ff[1:3, ]
data(submission_info)
#check some info about top 3 sumbissions
submission_info[1:3,]
```

## License

This package is free and open source software, licensed under GPL-3
